\section{Introduction} \label{sec introduction}


\subsection{Purpose}

The Design Document has the purpose to provide a functional description of the system. It defines the design of the software architecture, its components and their interactions, provided with the used algorithms and the user interfaces design. 

The document is written for project managers, developers, testers and quality assurance. It can be used for a structural overview to help maintenance and further development.


\subsection{Scope}

PowerEnJoy is a large-scale car-sharing service. It requires to perform excellently, to be secure, easily modifiable and as available as possible. Minding these necessities, in the following chapters will be shown how the system is structured and and which were the reasons that led to such decisions.
  
\subsection{Definitions, Acronyms, Abbreviations}

\begin{description}
	\item[DD:] Design Document.
	\item[RASD:] Requirements Analysis and Specification Document.
	\item[System:] the whole software system to be developed, comprehensive of all its parts.
	\item[REST:] REpresentational State Transfer. It's an architectural style and an approach to stateless communications, used in the development of client-server systems.
	\item[GUI:] Graphical User Interface.
	\item[ACID:] Atomicity, Consistency, Isolation, Durability. A set of properties of database transactions.
	\item[API:] Application Programming Interface.
	\item[EJB:] Enterprise Java Bean.
	\item[JPA:] Java Persistence API.
	\item[JSP:] JavaServer Pages.
	\item[HTTP:] HyperText Transfer Protocol.
	\item[HTTPS:] HyperText Transfer Protocol Secure.
\end{description}

\subsection{Reference Documents}

This document refers to the project rules of the Software Engineering 2 project~\cite{se-project-rules} and to the DD assignment~\cite{se-assignment}.

\subsection{Document Structure}

This document is structured in five parts:
\begin{description}
	\item[\autoref{sec introduction}: Introduction.] This section provides general information about the DD document and the used terms.
	\item[\autoref{sec architectural design}: Architectural Design.] This section shows the software architecture of the system, with its components and their interactions.
	\item[\autoref{sec algorithm design}: Algorithm Design.] This section will present and discuss in detail the algorithms designed for the system functionalities, independently from their concrete implementation.
	\item[\autoref{sec user interface design}: User Interface Design.] This section shows how the user interface will look like and behave, by means of concept graphics and UX modeling.
	\item[\autoref{sec requirements traceability}: Requirements Traceability.] shows how the requirements in the RASD~\cite{rasd} are satisfied by the design choices of the DD.
\end{description}