\section{Introduction} \label{sec introduction}

\subsection{Revision History}

Version of this document: 1.0 \\
Last update: 15/01/2017

\subsection{Purpose}

This document is the Integration Test Plan Document (ITPD) for the PowerEnJoy software. It describes the testing approach and overall framework that will drive the testing of the software.

The document is written for project managers, developers, testers and quality assurance.

\subsection{Scope}

PowerEnJoy is a digital management system for a car-sharing service. Its software need to be tested, in a clearly defined and well thought way, in order to avoid any failure or undesired behavior of the system.
  
\subsection{Definitions, Acronyms, Abbreviations}

\begin{description}
	\item[ITPD:] Integration Test Plan Document.
	\item[DD:] Design Document.
	\item[RASD:] Requirements Analysis and Specification Document.
	\item[System:] the whole software system to be developed, comprehensive of all its parts.
	\item[REST:] REpresentational State Transfer. It's an architectural style and an approach to stateless communications, used in the development of client-server systems.
	\item[GUI:] Graphical User Interface.
	\item[API:] Application Programming Interface.
	\item[EJB:] Enterprise Java Bean.
	\item[JPA:] Java Persistence API.
	\item[JSP:] JavaServer Pages.
	\item[HTTP:] HyperText Transfer Protocol.
	\item[HTTPS:] HyperText Transfer Protocol Secure.
\end{description}

\subsection{Reference Documents}

This document refers to the following documents:
\begin{itemize}
	\item Software Engineering 2 project~\cite{se-project-rules}.
	\item ITPD assignement~\cite{se-itpd}.
	\item RASD of the PowerEnJoy project~\cite{power-rasd}.
	\item DD of the PowerEnJoy project~\cite{power-dd}.
\end{itemize}

