\section{Introduction}

\subsection{Revision History}

Version of this document: 1.0 \\
Last update: 22/01/2017

\subsection{Purpose}

This document is the Project Plan Document (PPD) for the PowerEnJoy project. Its aim to estimate which are the sizes, the costs and the efforts that should be faced in order to realize the project. According to the estimation made, it will define the required budget, the resources allocation and the schedule of the activities.

The document is written for customers, project managers, developers, testers and all the stakeholders involved in the project implementation.

\subsection{Scope}

PowerEnJoy is a digital management system for a car-sharing service that exclusively employs electric car. This car rental system provides an alternative solution to public transport, thus being not only eco-friendly, but also simple and reliable. Its implementation should be achieved in a clear and defined way in order to meet the established deadlines, and avoid any further cost.

\subsection{Definitions, acronyms, and abbreviations}

\begin{description}
	\item[PPD:] Project Plan Document.
	\item[ITPD:] Integration Test Plan Document.
	\item[DD:] Design Document.
	\item[RASD:] Requirements Analysis and Specification Document.
	\item[System:] the whole software system to be developed, comprehensive of all its parts.
	\item[FSM:] Functional Size Measurement.
	\item[FP:] Function Point.
	\item[UFP:] Unadjusted Function Point.	
	\item[RET:] Record Element.	
	\item[DET:] Data Element.
	\item[ILF:] Internal Logic File.
	\item[EIF:] External Interface File.
	\item[EI:] External Input.
	\item[EQ:] External Inquiry.
	\item[EO:] External Output.
	\item[SLOC:] Source Line Of Code.
	\item[REST:] REpresentational State Transfer. It's an architectural style and an approach to stateless communications, used in the development of client-server systems.
	\item[GUI:] Graphical User Interface.
	\item[API:] Application Programming Interface.
\end{description}

\subsection{Reference Documents}

This document refers to the following documents:
\begin{itemize}
	\item Software Engineering 2 project~\cite{se-project-rules}.
	\item PPD assignement~\cite{se-ppd}.
	\item RASD of the PowerEnJoy project~\cite{power-rasd}.
	\item DD of the PowerEnJoy project~\cite{power-dd}.
	\item ITPD of the PowerEnJoy project~\cite{power-itpd}.
	\item COCOMO II - Model Definition Manual~\cite{cocomo}.
\end{itemize}