\section{Results of inspection}

\subsection{Notation}

\begin{itemize}
	\item A specific line of code will be referred as follows: L.1234.
	\item An interval of lines of code will be referred as follows: L.1234-5678.
\end{itemize}

\subsection{Issues}

\subsubsection{Naming Conventions}

\begin{enumerate}
	\item The name of the class is not meaningful - L. 45.
	\item The name of the variable \texttt{module} is not meaningful. It should be named \texttt{name} - L. 47.
\end{enumerate}

\subsubsection{Indentation}

\subsubsection{Braces}

\begin{enumerate}
	\item \texttt{if} statement without curly braces. - L. 107.
	\item \texttt{if} statement without curly braces. - L. 114.
	\item \texttt{if} statement without curly braces. - L. 116.
	\item \texttt{if} statement without curly braces. - L. 118.
	\item \texttt{if} statement without curly braces. - L. 122.
	\item \texttt{if} statement without curly braces. - L. 127.
	\item \texttt{if} statement without curly braces. - L. 134.
\end{enumerate}

\subsubsection{File Organization}

\begin{enumerate}
	\item Blank line not consistent - L. 48.
	\item Lines length exceed 80 characters. - L. 81-83.
	\item Missing blank line. - L. 83-84.
	\item Blank line not consistent. - L. 86.
	\item Blank line not consistent. - L. 104.
	\item Line length exceed 80 characters. - L. 105.
	\item Line length exceed 80 characters. - L. 107.
	\item Blank line not consistent. - L. 111.
	\item Lines length exceed 80 characters. - L. 113-118.
	\item Line length exceed 120 characters. - L. 121.
	\item Line length exceed 120 characters. - L. 126.
	\item Line length exceed 80 characters. - L. 132.
	\item Line length exceed 80 characters. - L. 134.
	\item Blank line not consistent. - L. 146.
	\item Line length exceed 80 characters. - L. 154.
	\item Line length exceed 80 characters. - L. 156.
\end{enumerate}

\subsubsection{Wrapping Lines}

\subsubsection{Comments}

Missing comments for all the methods.

\subsubsection{Java Source Files}

\begin{enumerate}
	\item Javadoc is incomplete for the method \texttt{getWrappedObject}. - L. 57.
	\item Javadoc is incomplete for the method \texttt{getArg}. - L. 65.
	\item Javadoc is incomplete for the method \texttt{getArg}. - L. 73.
	\item Javadoc is incomplete for the method \texttt{getWriter}. - L. 78.
\end{enumerate}

\subsubsection{Package and Import Statements}

\subsubsection{Class and Interface Declarations}

\subsubsection{Initialization and Declarations}

\begin{enumerate}
	\item Variable \texttt{redo} declared in the wrong scope. L. 110.
	\item Variable \texttt{subContentId} declared in the wrong scope. L. 113.
	\item Variable \texttt{contentId} declared in the wrong scope. L. 115.
	\item Variable \texttt{contentAssocTypeId} declared in the wrong scope. L. 117.
	\item Variable \texttt{lastComma} declared in the wrong scope. L. 139.
	\item Variable \texttt{lastPassedContentId} declared in the wrong scope. L. 140.
	\item Variable \texttt{nd} declared in the wrong scope. L. 149.
	\item Variable \texttt{firstTrailContentId} declared in the wrong scope. L. 150.
\end{enumerate}

\subsubsection{Method Calls}

\subsubsection{Arrays}

\subsubsection{Object Comparison}

\subsubsection{Output Format}

\subsubsection{Computation, Comparisons and Assignments}

\subsubsection{Exceptions}

\subsubsection{Flow of Control}

\subsubsection{Files}




